STAT 253 Final Project

### 2022-10-17 Final_Project_Work_HW2.Rmd
HW 3 Final

---
title: 'STAT 253 Final Project'
author: "Jacob, Julian, Aristo, and Emily"
date: "September 30, 2022"
output: 
  html_document:
    df_print: paged
    code_download: true
---

@@

```{r}
library(readr)
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
head(imdb_top_1000)
```

@@

# Update your models to use natural splines for some of the quantitative predictors to account for non-linearity (these are GAMs).

@@

# Compare insights from variable importance analyses here and the corresponding results from the Investigation

@@

# Compare model performance between your GAM models that the models that assuming linearity.

@@

# Summarize investigations

Decide on an overall best model based on your investigations so far. To do this, make clear your analysis goals. Predictive accuracy? Interpretability? A combination of both?

We want a combination of both, our spline model has the lowest RMSE but could be difficult to interpret. We need more visualization and analysis before we move forward. However we are confident in moving forward.

@@

Being that the data here is about movies, the harm that could come from our analysis would be minimal. 
Representation of different races, genders, abilities, etc. is an issue in Hollywood/the greater film industry, and it's likely that the harm our model/analysis produces is already in line with the issues that created and maintain this.
This is because the data we have is on past movies that have come out of this system. This means that whatever has made a movie successful, whether it's due to certain actors or directors, or whatever — this is a standard that has already existed. If we see the movies that have done really well because the cast is predominantly white, well this has been going on a for a long time because Hollywood is racist. Our model can't account for that, but we are aware of it.

>>>>

---
title: 'STAT 253 Final Project'
author: "Jacob, Julian, Aristo, and Emily"
date: "October 17, 2022"
output: 
  html_document:
    df_print: paged
    code_download: true
---

@@

```{r}
library(readr)
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
```

@@

# GAMs Using Splines

@@

# Variable Importance for GAM

@@

# Comparing Model Performance

@@

# Summarize Investigations

The goal of our investigations is to accurately predict a movie's gross box office revenue based on a number of predictors. We compared three different model types: ordinary linear regression (OLS) with all predictors, OLS using LASSO to select a subset of variables, and a GAM using splines to account for nonlinearity. The GAM model has the lowest RMSE but could be difficult to interpret. We are looking forward to continuing our investigations using Decision Trees which may offer a more easily interpreted method for modeling nonlinearity. Ideally, we would like an accurate model that is relatively easy to interpret.

@@

In addition to our earlier discussion of societal impacts that our model may have, we want to keep in mind the biases of the Hollywood movie industry. Representation of different races, genders, abilities, etc. is an issue in Hollywood/the greater film industry, and it is likely that the harm our model/analysis produces is already in line with the issues that created and maintain this. This is because the data we have is from past movies that came out of this system. This means that whatever made a movie successful, whether it's due to certain actors, directors, etc., is a standard that already existed. If we see the movies that have done really well have predominantly white casts, then it is likely a result of a longstanding issue of racism in the movie industry. Our model can't account for that, but we are aware of it.
